Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-14 latex/article.tex
abstract

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In article, we present a tool to
  efficiently explore the curvature tensor on the boundary of
  potentially large digital object. More precisely, we combine a fully
  parallel pipeline on GPU to extract an adaptive triangulated
  iso-surface of the digital object, with a curvature tensor
  estimation at each surface point based on integral invariants. Integral
  invariants being parametrized by a given ball radius, our proposal
  allows us to explore interactively different radii and thus select
  the appropriate scale to perform the computations (mean and gaussian
  curvature, principal curvatures, principal directions and normal
  vector field).

>>>>

\begin{abstract}\sloppy
  Interactive visualization is a very convenient tool to explore
  complex scientific data or to explore different parameter settings
  for a given processing algorithm. In this article, we present a tool
  to efficiently explore the curvature tensor on the boundary of
  potentially large digital objects. More precisely, we combine a
  fully parallel pipeline on GPU to extract an adaptive triangulated
  iso-surface of the digital object, with a curvature tensor
  estimation at each surface point based on integral
  invariants. Integral invariants being parametrized by a given ball
  radius, our proposal allows us to explore interactively different
  radii and thus select the appropriate scale to which the computation
  is performed and visualized (mean and gaussian curvature, principal
  curvatures, principal directions and normal vector field).
